maxent model avec xvalidation

### 2019-04-04 src/maxent_avec_xvalidation.Rmd
avg model results done

next step... select the models you want for each year and run those models again (primarily based on lowest AICc but check test AUC and other things too)

@@

ok! now to average results:
- the asc files per depth layer
- the AICforMaxentReg.csv 
- the maxentResults.csv

>>>>

#model selection
next step... select the models you want for each year and run those models again (primarily based on lowest AICc but check test AUC and other things too)

@@

#model averageing

ok! now to average results:

- the AICforMaxentReg.csv 
- the maxentResults.csv
- the asc files per depth layer

open all maxentReg files

```{r avg maxentReg}
#mth <- "jan"
#modelmonth <- cbind(paste0(mth, unique(janprback$year)))
for (i in 1:length(modelmonth)){
  timeslice <- modelmonth[i]
  yr <- str_sub(timeslice, -4) #the year being used for testing
  if(yr == 2003){
    aic2003 <- read.csv(paste0("../output/maxent/models/", timeslice, "/AICforMaxentReg.csv"), header = TRUE)
    } else if (yr == 2004){
    aic2004 <- read.csv(paste0("../output/maxent/models/", timeslice, "/AICforMaxentReg.csv"), header = TRUE)
    } else if (yr == 2005){
    aic2005 <- read.csv(paste0("../output/maxent/models/", timeslice, "/AICforMaxentReg.csv"), header = TRUE)
    } else if (yr == 2006){
    aic2006 <- read.csv(paste0("../output/maxent/models/", timeslice, "/AICforMaxentReg.csv"), header = TRUE)
  }
}

aic <- rbind(aic2003, aic2004, aic2005, aic2006)
aicm <- colMeans(aic)
aicm$mod <- "avg"
avgAIC <- rbind(aic, aicm)

write.csv(avgAIC, paste0("../output/maxent/models/", mth, "avgAIC.csv"), row.names = FALSE)
```

```{r avg maxres}
#mth <- "jan"
#modelmonth <- cbind(paste0(mth, unique(janprback$year)))
for (i in 1:length(modelmonth)){
  timeslice <- modelmonth[i]
  yr <- str_sub(timeslice, -4) #the year being used for testing
  if(yr == 2003){
    maxr2003 <- read.csv(paste0("../output/maxent/models/", timeslice, "/maxentResults.csv"), header = TRUE)
    } else if (yr == 2004){
    maxr2004 <- read.csv(paste0("../output/maxent/models/", timeslice, "/maxentResults.csv"), header = TRUE)
    } else if (yr == 2005){
    maxr2005 <- read.csv(paste0("../output/maxent/models/", timeslice, "/maxentResults.csv"), header = TRUE)
    } else if (yr == 2006){
    maxr2006 <- read.csv(paste0("../output/maxent/models/", timeslice, "/maxentResults.csv"), header = TRUE)
  }
}

maxr <- rbind(maxr2003, maxr2004, maxr2005, maxr2006)
maxr$Species <- 1
maxrm <- colMeans(maxr)
maxrm$Species <- "avg"
maxrm <- rbind(maxr, maxrm)

write.csv(maxrm, paste0("../output/maxent/models/", mth, "avgmaxentresults.csv"), row.names = FALSE)
```
